---
title: "Homework 10 - web scraping with rvest"
author: "Rowenna Gryba"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    keep_md: yes
---

# Scraping with `rvest`
## Read in required libraries
```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(rvest))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
```

## eBird website
In this first task I am taking the list of species that have undergone a taxonimic split and providing a table of which species they have been split into.

```{r}
#web scraping
split <- read_html("https://ebird.org/science/the-ebird-taxonomy") %>% 
	html_nodes("ul:nth-child(45) em:nth-child(1)") %>%
	html_text()

split <- tibble(split)

splitInto <- read_html("https://ebird.org/science/the-ebird-taxonomy") %>% 
	html_nodes("li:nth-child(1) em:nth-child(3) , ul:nth-child(45) em:nth-child(2)") %>%
	html_text()

splitInto <- tibble(splitInto)

#small data clean up for one of the genus names and divide the names into 2 columns
splitInto <- splitInto %>%
	separate(splitInto, c("genus", "sp2", "spp") , sep = " ") %>%
	mutate(genus = recode(genus, `O.` = "Oceanodroma"))

split <- split %>%
	separate(split, c("genus", "sp1"), sep = " ")

#join the tables
splitCombo <- full_join(split, splitInto, by = "genus") %>%
	mutate(SpSplit = paste(genus, sp1, sep = " "),
				 SpInto = paste(genus, sp2, spp, sep = " "))
	
splitCombo <- splitCombo %>%
	select(SpSplit, SpInto)

kable(head(splitCombo), format = "html") %>%
	kable_styling()
```

## James Bond actors
Next task with `rvest` will be to determine the number of times an actor has been in a James Bond movie and which role.
```{r}
jbActors <- read_html("https://www.the-numbers.com/movies/franchise/James-Bond#tab=summary") %>% 
	html_table() %>%
	.[[3]] %>%
	select(Person, `Nr. ofMovies`, Role)

kable(head(jbActors), format = "html") %>%
	kable_styling()
```

P.S. The reason I switched to James Bond is that the eBirds site is complicated!!! Going to try it with `httr` and see if it's any better.